### 2016-04-23 manuscript-body.tex
Augment introduction
turn bold type into typewriter type for meats and sandwich example

In 1996, learning scientist David Hammer argued ``Not all thoughts students express need to be understood as directly reflecting stable, stored knowledge structures. What the misconceptions perspective treats as a stored construct may alternatively be treated as an act of construction.'' \cite{hammer_misconceptions_1996}. In the 20 years since, researchers---particularly in science education---have pushed cognitive models beyond the static assumptions of classical misconception accounts of knowledge. But, a striking preponderance of computing education research models cognition via misconceptions. Such research assumes students have entrenched, wrong ideas about computation. And, while misconceptions research in computing education has advanced our understanding of teaching and learning, its narrow also begets problems growing too big to ignore:

@@

In this paper, we aim to start remedying those problems. We first reanalyze historical data using a knowledge-in-pieces perspective to show how we might recover accounts of students' productive knowledge. We then argue through example that expertise in programming can involve the fluid and active construction of conceptual metaphors to deal with idiosyncrasies within and across programming languages. These examples help broaden our sense of applicable cognitive theory by showing how distributed cognition can be a powerful framework for analyzing activity. Finally, we conclude with an exploration of epistemological concerns, arguing that a fundamental concern for our research community should be paying attention to what counts as knowledge and knowing in computing learning environments.

@@

we argue research
approaches that inflexibly privilege canonical knowledge do so at the
expense of other productive knowledge and ways of knowing that students
have.

@@

Again, the researchers are right that the student is failing to describe
the code in a way consistent with canon. But, in their non-canonical thinking Student3 evidences
potentially ``\emph{productive}'' \cite{hammer_form_2002,hammer_tapping_2003} insights about design. Precisely \emph{because}
there is no code stating that \textbf{turkey} and \textbf{roastBeef} and
ham are sorted into the array, the student is \emph{inferring} that to
be true. And, while that behavior is not what's happening, it
\emph{would} be sensible to design a program where specific instances of
classes \textbf{Turkey} and \textbf{Ham} and \textbf{RoastBeef} could go
into an array of type \textbf{Meat}. To do so, a designer could define
\textbf{Turkey} and \textbf{Ham} and \textbf{RoastBeef} as inheriting
from \textbf{Meat}.

>>>>

Science and math education started challenging misconception models of mind in 1993 \cite{disessa_epistemology_1993,smith_misconceptions_1993}. By 1996, learning scientists were boldly repudiating the assumptions of misconceptions: ``Not all thoughts students express need to be understood as directly reflecting stable, stored knowledge structures. What the misconceptions perspective treats as a stored construct may alternatively be treated as an act of construction.'' \cite{hammer_misconceptions_1996}. In the more than 20 years since those papers were published, researchers---particularly in science education---have pushed cognitive models beyond the static assumptions of classical misconception accounts of knowledge. But, a preponderance of research in computing education (CSEd) has modeled and continues to model cognition through misconceptions. Such research assumes students have entrenched, wrong ideas about computation. And, while misconceptions research in computing education has advanced our understanding of teaching and learning, its narrow focus also begets problems that are growing too big to ignore:

@@

This paper aims squarely at those problems by expanding a sense of what's possible in modeling cognition within computing education research. We argue research
approaches that inflexibly privilege canonical knowledge do so at the
expense of other productive knowledge and ways of knowing that students
have. First, we reanalyze prior data to show how we might recast misconceptions as the potential seeds of productive knowledge. We then argue through example that expertise in programming can involve the fluid and active construction of conceptual metaphors to deal with idiosyncrasies within and across programming languages. These examples help broaden our sense of applicable cognitive theory by showing how distributed cognition and symbolic forms can be a powerful framework for analysis in CSEd. Finally, we conclude with an exploration of epistemological concerns, arguing that a fundamental concern for our research community should be paying attention to what counts as knowledge and knowing in computing learning environments.

@@

@@

Again, the researchers are right that the student is failing to describe
the code in a way consistent with canon. But, in their non-canonical thinking Student3 evidences
potentially ``\emph{productive}'' \cite{hammer_form_2002,hammer_tapping_2003} insights about design. Precisely \emph{because}
there is no code stating that \texttt{turkey} and \texttt{roastBeef} and
ham are sorted into the array, the student is \emph{inferring} that to
be true. And, while that behavior is not what's happening, it
\emph{would} be sensible to design a program where specific instances of
classes \texttt{Turkey} and \texttt{Ham} and \texttt{RoastBeef} could go
into an array of type \texttt{Meat}. To do so, a designer could define
\texttt{Turkey} and \texttt{Ham} and \texttt{RoastBeef} as inheriting
from \texttt{Meat}.
